
\chapter{AWIPS Architecture and Implementation Guide}

This section provides guidance to developers on how to
implement new functionality for AWIPS.  It includes:
\begin{itemize}
\item
A high-level view of the AWIPS architecture;
\item
Case studies -- complete implementations of typical
functionality;
\item
Interface descriptions;
\item
How to find utilities and libraries.
\end{itemize}


\section{High-Level View of AWIPS Architecture}

There must be other documents that describe this in detail,
and this section might reference them.
But the main components of the architecture should be described here.

\begin{itemize}
\item What are the major architectural components of AWIPS?
\item In the context of CAVE, what is a plugin?
\item In the context of EDEX, what is a plugin?  
\item What does the ESB do in AWIPS2?
\item What components are re-wrapped legacy code?
\item And so on
\item And so forth
\end{itemize}


\section{Data Ingest and Access}

What do you have to do to add a new set to AWIPS2?  Ingest?  Storage? 
Access?  Display?  Notifications?  Ingest monitoring and alarming?

\section{Command Line Interface}

CLI Capabilities.  

\section{Event Handling}

Describe messaging capability that delivers system and user 
events such as GUI actions, grid changes, error messages, 
text product completion and other internal and external events.

How processes register for event notifications.

Mouse events - Examples of how A-II handles mouse events and 
context-sensitive mouse events, in particular.

Keyboard accelerators.

Event notification for display changes - Pane swaps, changing frame 
count, display layers.


\section{CAVE Plugins}

How to create a CAVE plugin.  An important part of this section 
will be at least one low level, detailed, step-by-step procedure for 
creating an example plugin.  But the section needs to contain much more 
than that.  In addition to the detailed procedure it must contain a 
coherent, complete description of the architecture within which CAVE 
plugins exist.  Files must be identified and their purposes explained.


\section{EDEX Plugins}

Same kind of content as the subsection on CAVE Plugins.


\section{GUI Style and API}

TBD:  Not sure what kind of thing goes in here.  Steve mentioned 
"GUI API".  The API for constructing GUIs is really Eclipse
and the Standard Widget Toolkit (SWT).  There may be some
AWIPS-specific GUI APIs.  For example to add an item to a
data selection menu.  Might also be useful to put in some
``style'' guidance similar to the old Motif Style Guide,
which described provided information to standardize look and
feel and promote usability in Motif GUIs.

TBD: How to add online help.  Adding a help option on the main
menu bar.  Adding a help button on a widget.


\section{Hydromet Libraries}

TBD:  Best not to list specific functions or files here.  It 
would be hard to keep it up to date.  Better to give a high
level description of the architecture of the hydromet libraries
and any commonality there might be in their interfaces.  Then 
provide some kind of pointer into the code.  Maybe one or more
package names?

\section{Coordinate Transformations}

TBD: As for hydromet libraries.  High-level discussion, direct
people to code for listings of functions and interfaces.

\section{Units and Unit Conversions}

TBD: As for hydromet libraries.  High-level discussion, direct
people to code for listings of functions and interfaces.

\section{Image Processing}

TBD: As for hydromet libraries.  High-level discussion, direct
people to code for listings of functions and interfaces.

\section{Errors, Exceptions, and Logging}

TBD: Policies, tools, etc. for handling errors, exceptions, logging.






