
\chapter{Introduction}

An important goal of the AWIPS Evolution project is
to make
new science, technology, and research results available at
the forecaster's workstation with minimal delay.

That will require the AWIPS software development
process and environment to support and encourage
collaborative development including contributions from NOAA
development organizations, proving grounds, test beds, 
and academic and research communities.  We must provide as direct
and rapid a
path as possible from the researcher to the AWIPS
operational code baseline.

The
challenge in doing that is to develop streamlined governance processes
balancing software agility needs with necessary software engineering
discipline to ensure the infusion of high quality software 
into the AWIPS baseline.


This Handbook and associated documents will document a 
software development process and environment intended to meet
those requirements.  

The process description will include work flow procedures,
coding standards, documentation requirements, and
implementation guidelines.  

As well as defining the software
development process, the Handbook will describe the software
development environment (software ``stack'') provided to facilitate 
the process.  The software development environment should
minimize the burden the process imposes on developers.  The
Handbook should provide developers the information they need
to use the development environment efficiently.
That information may be provided by including it in the
Handbook or by reference to other documents.

Thus, the reader should expect to find descriptions of the following
in this Handbook, or included from other documents by reference:
\begin{itemize}
\item
Software development process
\item
Software development environment
\item
Project coding guidelines
\item
Important software development tools
\item
Overview of AWIPS architecture
\item
HowTo templates and examples for classes of development
tasks, including acceptable methods for accessing
infrastructure components
\end{itemize}

Please direct 
comments on this Handbook and requests for changes to
to the document maintainer (stowell.davison@noaa.gov).

This Handbook is maintained as a set of \LaTeX\ files in
the team's
Subversion repository.  The global revision
number of this version is in the Revision History
table at the front of the document.
The most recent version is available from the repository.




