
\subsection{How To Edit this Handbook}
 
Source file: AiiDhSwEnUsHb.tex

This Handbook is maintained in the Subversion
repository as a set of \LaTeX\ files.
Members of the AWIPS development community are encouraged to
submit suggestions for additions, deletions, or changes to
the AWIPS Development Guidelines Working Group.  You can 
send suggestions to 
the document maintainer, whose email address appears in the
Introduction.
 
You can also edit the Handbook directly, but please
coordinate with the document maintainer before checking
anything in to the main trunk of the Subversion repository.

On the other hand, you can check anything you like in to
your own branch of the repository (how to create that branch
is described below).  Editing the Handbook is a good way to
get some familiarity with Subversion operations.
 
You will need package tetex-latex installed on your
computer.  If you want to build the html version of the
document you will also need package latex2html.  Both are
available from the Red Hat or CentOS repositories.

\begin{verbatim}
    # ----- Set an environment variable for the URL of the repository.
    export URL=http://swdavison.dyndns.org:8080/awips2_repo/AiiDh

    # ----- Make a branch of the Subversion for yourself.
    svn copy $URL/trunk $URL/branches/<yourNameHere> -m"New branch"

    # ----- Check the source code out of your new branch.
    mkdir ~/workarea
    cd ~/workarea
    svn checkout $URL/branches/<yourNameHere>

    # ----- Build the document.
    ./build.sh
\end{verbatim}

The build process generates several intermediate files and two
final build products: AiiDh.pdf and the AiiDh subdirectory.
You can inspect the first with any PDF reader (acroread, gs,
etc.).  The AiiDh directory contains the HTML version of the
Handbook, which you can inspect with any web browser.

Now you can edit the tex files with any text editor, rebuild
the document, and inspect the results.  At any time you can
check your work in:
\begin{verbatim}
    svn commit -m"checkpoint save"
\end{verbatim}

You may be able to learn what you need to know about
Latex markup by inspecting the source code files for the
Handbook and comparing them with the built result (PDF or
HTML).  If you want more information please see the 
section titled ``Appendix \ref{ReferencesAndResources}: References and Resources.''
% section titled Appendix \hyperref[ReferencesAndResources]{References and Resources}.
In particular, there
is link to a downloadable book from Wikibooks.  (Search for
``wikibooks.'')

See the section titled ``How To Deliver Code'' for instructions on 
how to merge your branch back in to the trunk so that the
Hudson build posts your new version on the team wiki.  But
please coordinate that delivery with the document maintainer
ahead of time.



