
\section{Using the Software Development Environment}

How to use Subversion and Trac (oriented toward devlopers,
not administrators).  ADE setup defined by Raytheon flowtag.  
Include by reference.  All Java development takes place within the 
Eclipse/ADE environment.

How to use the SDE software.  Step by step instructions for check 
in, check out, merge, deploy.  Generally organized to support the 
software development process section.

Perhaps incorporate here the HowToWiki from the NCLADT wiki 
(\url{https://collaborate.nws.noaa.gov/trac/ncladt/wiki/HowToWiki}).  
Some of it should be in the software development process 
section.  Example: Create a wiki 
page if you create an app (or new user-level function).  The wiki
has the potential to be a powerful communications tool if we 
can define good policies early and stick to them.  Need to 
learn some lessons from the NCLADT.  Note also that Trac provides a specific
mechanism for making inter-wiki links.  
\url{https://collaborate.nws.noaa.gov/trac/ncladt/wiki/InterWiki}

TBDs:
\begin{itemize}
\item
Document templates
\item
HowTo initialize a ticket
\item
HowTo schedule ticket to a build
\item
HowTo assign ticket to developer
\item
HowTo attach documents to ticket
\item
HowTo add comments with ticket number to source code so that 
Subversion hooks interact properly w/ Trac to link tickets
to specific code revision numbers.
\item
Needs thinking, discussion about how to set up 
the ticket categories, life cycles, roles, in Trac.  We
really won't know for sure until we start doing it.
\end{itemize}

% ----- Working with Subversion
\input{AiiDhSwEn/AiiDhSwEnUsSu}

% ----- How To Edit this Handbook
\input{AiiDhSwEn/AiiDhSwEnUsHb}

% ----- How To Create a New Development Branch
\input{AiiDhSwEn/AiiDhSwEnUsDb}

% ----- How To Update a Branch from the Trunk
\input{AiiDhSwEn/AiiDhSwEnUsUb}

% ----- How To Deliver Code to the Trunk
\input{AiiDhSwEn/AiiDhSwEnUsDc}



