
\chapter{Software Development Environment}

The software development environment (SDE) is a set of tools to 
minimize the burden imposed on developers and management by 
the software development process.  In the context of this 
document the SDE is the set of 
tools (a software ``stack'') used by one or more software 
development teams.  The AWIPS II development environment for 
individual programmers is defined by the AWIPS Development 
Environment (ADE) package delivered and documented by Raytheon 
as part of the AWIPS Migration project.

On the server side, the SDE consists of:
\begin{itemize}
\item
Subversion.  The source code management system.
\item
Trac.  The wiki and issue tracking system.
\item
Hudson.  The build management system.
\end{itemize}

Please see the section titled ``References and Resources''
for links and references to more information on those 
server-side components.  The section titled
``Installing the Software Development Environment''
describes how to install them.

On the client side, the SDE consists of:
\begin{itemize}
\item
Firefox.  Any other web browser should work.  The web
browser serves as the client for the Subversion, Trac, and
Hudson servers.
\item
ADE.  This is the AWIPS Development Environment, which is
delivered with each AWIPS release by Raytheon.  It includes
Eclipse.
\item
Svn.  This is the Subversion command line client.  The
version of Eclipse included with the ADE has a built-in
Subversion client (the Subclipse plugin), but users who want
to have the full power of Subversion available will want to
use svn.  Svn is also very well documented in the ``Red
Book.''  (Please see the section titled ``References and
Resources'' for a link to that book.)
\end{itemize}


\input{AiiDhSwEn/AiiDhSwEnAd.tex}

\input{AiiDhSwEn/AiiDhSwEnUs.tex}


