
\section{Introduction}

Source file: AiiDhAppInstIntro.tex

This document describes a proposed software development environment for
the SEC AWIPS Software Development Team.  NCEP's development environment
served as a model for this one, and NCEP's environment was patterned
after the one used by the Raytheon AWIPS II development team in Omaha.

Features of the software development environment:
\begin{itemize}
\item
Integrated with Eclipse.  Eclipse GUIs support code check out and check in.

\item
Distributed.  Clients (Eclipse, for example) can be on machines remote from the source code repository.  Builds can be started, monitored, and stopped from remote machines.

\item
Automated building.  The build management system can be configured to start a build whenever the source code changes; or can be configured to check periodically (every hour, for example) to see if the source code has changed and start a build if it has.

\item
Web browser based build control.  Builds can be started, monitored, and stopped using a web browser.

\item
Build and configuration linkage.  For every build it is possible to determine the version of every source code document.

\item
Issue tracking.  Work assignments and discrepancy reports can  be entered, modified, and tracked using a web browser interface.  Life cycles can be defined.

\item
Linkage of source code changes and change authorization documents.
The system can be configured so that any source code change that is
checked in must be linked to a change authorization document in an
appropriate life cycle stage.

\item
Version control system supports branching, merging, and tagging.

\item
All open source.  No software licenses, license manager daemons, seat
count limitations, expiration dates, etc.

\end{itemize}

At a high level, the development environment software stack consists of
Eclipse, Subversion, Hudson, and Trac.

Eclipse is the integrated development environment (IDE) delivered by
Raytheon as part of the AWIPS Development Environment (ADE) package.
The version of Eclipse that Raytheon provides with the ADE includes
the Subclipse plugin, which provides individual developers with
a convenient interface for checking source code in and out of the
Subversion repository.

Subversion is the version and configuration management tool.  Subversion
has its own server, but in this configuration we are not using it.
Instead, the Apache httpd web server acts as the Subversion server.
Subversion also has its own client: svn.  

Hudson is a build management tool.  In ths development environment
Hudson builds AWIPS automatically when new source code revisions are
checked in to the Subversion repository.  Hudson is also web-accessible,
so builds may be started and monitored remotely, as long as the remote
machine can make an http connection to the build machine.  Hudson is
another Subversion client.

Trac is an issue tracking and wiki tool.  In the context of Trac, an
"issue" can be anything that has a life cycle and must be tracked.
Examples include bug reports and work assignments.  NCEP's software
development process uses Trac to track software development tasks.

The NCEP development environment includes another component, USVN, which
provides a web browser interface for administration of the Subversion
repository.  A description of USVN setup will be included in  a later
version of this document.

These software components are used in numerous free and open
source projects.  They have active web sites and, in most cases, good
documentation.  For more information on them please see the sites listed
in the "References and Resources" section of this document.

Much of this document consists of sequences of Unix commands.  The reader
may be tempted to treat those sequences as scripts and execute them
accordingly.  In many cases that would be a mistake.  The command
sequences are intended as procedure descriptions; Unix command lines
are used as convenient, unambiguous ways of presenting the procedures.
In most cases it would be safe (and probably efficient) to copy-and-paste
the commands to save typing.  But some commands will have to be modified.

